### 2021-07-21 doc/thesis/chapters/implementation.tex
update

@@

A testbench is equally important in the HLS implementation, as it is for the VHDL implementation, explained in \ref{sub:VHDL:Testbench:General}.
The testbench simulation is

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{TODO: Other Stuff...}

@@

A testbench is equally important in the HLS implementation, as it is for the VHDL implementation.
Just like the IPs' HDL code, the testbench is also written in the language \cplusplus.
The execution of the testbench is done in the Xilinx HLS software.

A major difference between a VHDL testbench and a HLS testbench is its execution speed.
HLS faster because it does not simulate any timing info; its just plain c++ code thats run

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design for Reuse}

testbench is using Firmware code! --> enables reuse and early testing on the code, before a hardware prototype exists
